### 2020-06-18 Strings2020/strings6/strings6.tex
Update strings6

\newcommand{\NS}{\ensuremath{\mrm{NS}}}
\newcommand{\R}{\ensuremath{\mrm{R}}}

@@

	A closed superstring theory consists of sectors labeled by the boundary conditions of $(\psi,\tilde{\psi})$ along with suitable GSO projections $(-1)^F = \pm 1$. Here we follow the discussions of \textit{Polchinski}, with $\mrm{R}\colon \alpha = 1$ and $\mrm{NS}\colon \alpha = 0$.

	There are also some consistency conditions: by modular invariance, there must be at least one left-moving R sector and at least one right-moving R sector; on the other hand, the OPE must close, and since $\mrm{R} \times \mrm{R} = \mrm{NS}$ there must be corresponding NS sector for each R sector.

	If we includes only the (NS, NS) and the (R, R) sectors, then both must exist due to the above conditions. In fact, closure of OPE implies that the (\,NS$+$, NS$+$) sector must exist. In addition, NS$-$ sector must be paired with another NS$-$ sector due to the level matching condition of the closed string, i.e. it is possible to have a (\,NS$-$, NS$-$) sector.

	The full possiblities can be generated by enumerating all possible (R, R) sectors (there is $2\times 2 = 4$ of them), while applying an extra consistency check that all pairs of vertex operators $O_1,O_2$ are mutually local, i.e.
	\begin{equation}
		\exp i\pi \pqty{
				  F_1 \alpha_2
				- F_2 \alpha_1
				- \tilde{F}_1 \tilde{\alpha}_2
				+ \tilde{F}_2 \tilde{\alpha}_1
			}
		= 1
	\end{equation}
	If $O_1 \in (\,\NS+, \NS+)$, then we have $\alpha_1 = \tilde{\alpha}_1 = 0 = F_1 = \tilde{F}_1$, hence the above factor is always trivial; for $O_1 \in (\R,\R)$, however, $\alpha_1 = \tilde{\alpha}_1 = 1$, which yields a non-trivial constraint for the second operator: $
		F_2 - \tilde{F}_2
		= F_1 \alpha_2 - \tilde{F}_1 \tilde{\alpha}_2
		= \alpha_2 \pqty\big{F_1 - \tilde{F}_1}
		\ (\mop{mod} 2)
	$, assuming $\alpha_2 = \tilde{\alpha}_2$. With $\alpha_2 = 0$ this gives $F_2 = \tilde{F}_2$, and with $\alpha_2 = 1$ this gives $
		F_2 - \tilde{F}_2
		= F_1 - \tilde{F}_1
	$, which means that all (R, R) sectors have the same sign difference between $F$ and $\tilde{F}$. The possible solutions can then be narrowed down to:
	\begin{gather}
		\mrm{0A}\colon\ %
			(\,\NS+,\NS+),\ %
			(\,\NS−,\NS−),\ %
			(\,\R+,\R-),\ %
			(\,\R−,\R+), \\
		\mrm{0B}\colon\ %
			(\,\NS+,\NS+),\ %
			(\,\NS−,\NS−),\ %
			(\,\R+,\R+),\ %
			(\,\R−,\R−), \\
		\text{And additionally, $(\,\NS+,\NS+)$ with any \textit{single one} of the 4 possible (R, R) sectors.}
	\end{gather}

	If there are two (R, R) sectors, then there must be an acompanying $(\,\NS−,\NS−)$ sector due to the closure of OPE. It is straight-foward to check that these possiblilities are all valid under the above constaints: (0) level matching of closed strings, (1) mutual locality, (2) closure of OPE, and (3) (apparent) modular invariance (not sufficient yet, to be checked below).

@@

	Similar to the Type II case, the building block of $Z$ is given by:
	\begin{equation}
		Z\id{^\alpha_\beta}
		= \Tr_\alpha \bqty{
				(-1)^{\beta F} q^H
			}
	\end{equation}
	Where $\alpha,\beta$ labels the periodicity in the spatial and temporal directions ($\sigma^1,\sigma^2$); note that for fermionic fields, anti-periodicity in the time direction gives the simple trace, while the periodic path integral gives the trace weighted by $(−1)^F̂$, as is explained in \textit{Polchinski}, Appendix A. 
	\end{enumerate}

>>>>

% NS & R with spacing
\newcommand{\NS}{\ensuremath{\mspace{2mu}\mrm{NS}}}
\newcommand{\R}{\ensuremath{\mspace{2mu}\mrm{R}}}

% representations
\newcommand{\mbf}[1]{\mathbf{#1}}

@@

	A closed superstring theory consists of sectors labeled by the boundary conditions $(-1)^\alpha$ of $(\psi,\tilde{\psi})$ along with suitable GSO projections $(-1)^F = \pm 1$. Here we follow the discussions of \textit{Polchinski}, with $\mrm{R}\colon \alpha = 1$ and $\mrm{NS}\colon \alpha = 0$.

	There are also some consistency conditions: by modular invariance, there must be at least one left-moving R sector and at least one right-moving R sector; on the other hand, the OPE must close, and since $\mrm{R} \times \mrm{R} = \mrm{NS}$ there must be some corresponding NS sector for each R sector.

	If we includes only the (NS, NS) and the (R, R) sectors, then both must exist due to the above conditions. In fact, closure of OPE implies that the $(\NS+, \NS+)$ sector must exist. In addition, NS$-$ sector must be paired with another NS$-$ sector due to the level matching condition of the closed string, i.e. it is possible (but not required) to have a $(\NS-, \NS-)$ sector.

	The full possiblities can then be generated by enumerating all possible (R, R) sectors (there are $2\times 2 = 4$ of them), while applying an extra consistency check that all pairs of vertex operators $O_1,O_2$ are mutually local, i.e.
	\begin{equation}
		\exp i\pi \pqty{
				  F_1 \alpha_2
				- F_2 \alpha_1
				- \tilde{F}_1 \tilde{\alpha}_2
				+ \tilde{F}_2 \tilde{\alpha}_1
			}
		= 1
	\end{equation}
	If $O_1 \in (\,\NS+, \NS+)$, then we have $\alpha_1 = \tilde{\alpha}_1 = 0 = F_1 = \tilde{F}_1$, hence the above factor is always trivial; for $O_1 \in (\R,\R)$, however, $\alpha_1 = \tilde{\alpha}_1 = 1$, which yields a non-trivial constraint for the second operator: $
		F_2 - \tilde{F}_2
		= F_1 \alpha_2 - \tilde{F}_1 \tilde{\alpha}_2
		= \alpha_2 \pqty\big{F_1 - \tilde{F}_1}
		\ (\mop{mod} 2)
	$, assuming $\alpha_2 = \tilde{\alpha}_2$. With $\alpha_2 = 0$ this gives $F_2 = \tilde{F}_2$, and with $\alpha_2 = 1$ this gives $
		F_2 - \tilde{F}_2
		= F_1 - \tilde{F}_1
	$; this means that all (R, R) sectors have the same sign difference between $F$ and $\tilde{F}$. The possible solutions can then be narrowed down to:
	\begin{gather}
		\mrm{0A}\colon\ %
			(\NS+,\NS+),\ %
			(\NS−,\NS−),\ %
			(\R+,\R-),\ %
			(\R−,\R+), \\
		\mrm{0B}\colon\ %
			(\NS+,\NS+),\ %
			(\NS−,\NS−),\ %
			(\R+,\R+),\ %
			(\R−,\R−), \\
		\text{And additionally, $(\NS+,\NS+)$ with any \textit{single one} of the 4 possible (R, R) sectors.}
		\label{eq:type0_deviant}
	\end{gather}

	If there are two (R, R) sectors, then there must be an acompanying $(\NS−,\NS−)$ sector due to the closure of OPE. It is straight-foward to check that these possiblilities are all valid under the above constaints: (0) level matching of closed strings, (1) mutual locality, (2) closure of OPE, and (3) (apparent) modular invariance (not sufficient yet, to be checked below).

@@

	Similar to the Type II case, the building block of $Z$ is given by:
	\begin{equation}
		Z\id{^\alpha_\beta}
		= \Tr_\alpha \bqty{
				(-1)^{\beta F} q^H
			},\quad
		q = e^{2\pi i\tau}
	\end{equation}
	Where $\alpha,\beta$ labels the periodicity in the spatial and temporal directions ($\sigma^1,\sigma^2$); note that for fermionic fields, anti-periodicity in the time direction gives the simple trace, while the periodic path integral gives the trace weighted by $(−1)^F̂$, as is explained in \textit{Polchinski}, Appendix A.

	In 10\,D, $\mu = 1,\cdots,10$, in total there are $
		N = 10 - 2 = 4\times 2 = 8
	$ real, \textit{transverse} spinor components in $(\psi^\mu,\tilde{\psi}^\mu)$; pairing them into complex chiral spinors like $\psi^1 \pm \psi^2$, each one of them contributes a factor of $Z\id{^\alpha_0}$ in the total partition function.

	Note that for type II theories, the boundary conditions and GSO projections $(\alpha,F)$ for the left and right movers are ``decoupled''; any possible $(\alpha,F)$ can be paired with any possible $(\tilde{\alpha},\tilde{F})$, hence the left and right contributions can be calculated separately. For type 0 theories, however, the left and right $(\alpha,F)$'s are coupled, hence we have to calculate their contributions together. With the above considerations, we have:
	\begin{equation}
	\renewcommand{\NS}{\mrm{NS}} % no spacing
	\renewcommand{\R}{\mrm{R}}   % no spacing
	\begin{aligned}
		\Tr_{(\NS,\NS)} \bqty{
				\frac{1 + (-1)^{F-\tilde{F}}}{2}\,
				q^H
			}
		&= \frac{1}{2}\, \Bqty\Big{
				\Tr_{(\NS,\NS)} q^H
				+ \Tr_{(\NS,\NS)}
					\bqty{(-1)^{F-\tilde{F}} q^H}
			} \\
		&= \frac{1}{2}\, \Bqty{
				\abs{(Z\id{^0_0})^{N/2}}^2
				+ \abs{(Z\id{^0_1})^{N/2}}^2
			} \\
		&= \frac{1}{2}\, \Bqty{
				\abs{Z\id{^0_0}}^N
				+ \abs{Z\id{^0_1}}^N
			},
	\\[2ex]
		\Tr_{(\R,\R)} \bqty{
				\frac{1 \mp (-1)^{F-\tilde{F}}}{2}\,
				q^H
			}
		&= \frac{1}{2}\, \Bqty\Big{
				\Tr_{(\R,\R)} q^H
				\mp \Tr_{(\R,\R)}
					\bqty{(-1)^{F-\tilde{F}} q^H}
			} \\
		&= \frac{1}{2}\, \Bqty{
				\abs{Z\id{^1_0}}^N
				\mp \abs{Z\id{^1_1}}^N
			},
	\end{aligned}
	\end{equation}
	\begin{equation}
		Z^{\mrm{0A|B}}
		= \frac{1}{2}\, \Bqty{
				\abs{Z\id{^0_0}}^N
				+ \abs{Z\id{^0_1}}^N
				+ \abs{Z\id{^1_0}}^N
				\mp \abs{Z\id{^1_1}}^N
			}
	\end{equation}
	Similarly, for the situation in \eqref{eq:type0_deviant} with no $(\NS-,\NS-)$ sector, 
	depending on the GSO projections $(F,\tilde{F})$ in the single (R, R) sector, we have:
	\begin{equation}
	\let\bar\overline
	\footnotesize
	\begin{aligned}
		Z'
		&= \abs{\frac{1}{2}\,\pqty{
				(Z\id{^0_0})^{N/2}
				+ (Z\id{^0_1})^{N/2}
			}}^2
			+ \frac{1}{2}\,\pqty{
				(Z\id{^1_0})^{N/2}
				+ (-1)^F (Z\id{^1_1})^{N/2}
			}
			\cdot \frac{1}{2}\,\pqty{
				(Z\id{^1_0})^{N/2}
				+ (-1)^{\tilde{F}} (Z\id{^1_1})^{N/2}
			}^* \\
		&= \frac{1}{2}\, \Bqty{
				Z^{0A|B}
				+ \Re\,
					(Z\id{^0_0} \bar{Z\id{^0_1}})^{N/2}
				+ (-1)^{\tilde{F}} \pqty{\Re| \,i\Im}\,
					(Z\id{^1_0} \bar{Z\id{^1_1}})^{N/2}
			}
	\end{aligned}
	\end{equation}

	To check for modular invariance, note that\footnote{
		See \textit{Polchinski}, Chapter 10. Note that the factor $
			\exp \pqty{
				- i\pi\, \frac{3\alpha^2 - 1}{12}
			}
		$ comes from a global gravitational anomaly, but does not matter in $Z^{0A|B}$ since we are taking absolute values. 
	}:
	\begin{equation}
		Z\id{^\alpha_\beta}(\tau)
		= Z\id{^\beta_{-\alpha}}(-\tfrac{1}{\tau})
		= Z\id{^\alpha_{\alpha + \beta - 1}}(\tau + 1)\,
			\cdot \exp \pqty{
				- i\pi\, \frac{3\alpha^2 - 1}{12}
			}
	\end{equation}
	We see that $Z^{0A|B}$ is indeed modular invariant, while $
		Z' = \frac{1}{2} Z^{0A|B}
			+ \pqty{\cdots}
	$ is \textit{not} modular invariant, due to the extra ``mixing'' terms in $(\cdots)$.

	\item Consider the ground states in the type 0 theories; the NS ground state is tachyonic: 
	\begin{equation}
		m^2 = -k^2 = -\frac{1}{2\alpha'}
	\end{equation}
	With $(-1)^F = -1$, while the level 1 states are massless and form a vector representation $\mbf{8}_v$ of the massless little group $\mrm{SO}(8)$. After GSO projections, the NS ground state becomes the (NS$-$) ground state, while the level 1 massless states become the (NS$+$) ground states.

	On the other hand, the R ground state is massless. In general, 10\,D Dirac spinors form a representation $\mbf{32}_{\mrm{Dirac}}$ of $\mrm{SO}(9,1)$; however, in the massless case it can be further reduced into two Weyl spinors $\mbf{16} + \mbf{16}'$, labeled by chirality $\Gamma^{11} = (-1)^F$. They are spinor representations of $\mrm{SO}(8)$. The on-shell condition (i.e.\ the Dirac equation) further reduces the representation into $\mbf{8}$ and $\mbf{8}'$, one for $(\R+)$ and one for $(\R-)$.

	The closed string spectrum is then obtained by tensor product of the left and right moving part. For type 0 theories, we see that there is a tachyonic state: the $(\NS-,\NS-)$ ground state is a $\mbf{1}\times \mbf{1} = \mbf{1}$ scalar tachyon; with a momentum rescale $k\mapsto k/2$, the mass is now given by $m^2 = -2/\alpha'$. The remaining massless states are:
	\begin{alignat}{2}
		(\NS+,\NS+)\colon&\quad&
			\mbf{8}_v \times \mbf{8}_v
			&= [0] + [2] + (2) \\
		(\R\pm,\R\pm)\colon&&
			\mbf{8}^{(\prime)} \times \mbf{8}^{(\prime)}
			&= [0] + [2] + [4]_\pm \\
		(\R+,\R-)\colon&&
			\mbf{8} \times \mbf{8}'
			&= [1] + [3]
	\end{alignat}
	Where we've listed the irreducible decompositions of the various $\mbf{8} \times \mbf{8}$ tensor product, following the notations of \textit{Polchinski}.

	\item \textbf{Kaluza--Klein Mechanism}

	The $D = d+1$ dimensional metric can be parameterized as follows:
	\begin{gather}
		\dd{s}^2
		= G_{MN}^D \dd{x^M} \dd{x^N}
		= G_{\mu\nu} \dd{x^\mu} \dd{x^\nu}
			+ e^{2\sigma}\,\pqty{
				\dd{x^d} + A_\mu \dd{x^\mu}
			}^2,
	\\
		G^D_{\mu\nu}
		= G_{\mu\nu} + e^{2\sigma} A_\mu A_\nu,\quad
		x^d \cong x^d + 2\pi R
	\end{gather}
	Where $\mu = 0,1,\cdots,(d-1)$ labels the noncompact directions, and the $x^d$ direction is compactified. $G_{\mu\nu},\sigma$ and $A_\mu$ should depend only on the noncompact coordinates $x^\mu$, $A^\mu = G^{\mu\nu} A_\nu$.

	$G_{MN}^D$ can be inverted by solving $
		\delta^L_N
		= G^{LM}_D G^D_{MN}
	$, or in components:
	\begin{gather}
		0 = G_D^{\mu\nu}\, e^{2\sigma} A_\nu
			+ G_D^{\mu d}\, e^{2\sigma}
	\quad\Longrightarrow\quad
		G_D^{\mu d}
		= - G_D^{\mu\nu} A_\nu,
	\\
		1 = G_D^{\mu d}\, e^{2\sigma} A_\mu
			+ G_D^{dd}\, e^{2\sigma}
	\quad\Longrightarrow\quad
		G_D^{dd}
		= e^{-2\sigma} - G_D^{\mu d} A_\mu
		= e^{-2\sigma} + G_D^{\mu\nu} A_\mu A_\nu,
	\\
		\delta^\mu_\rho
		= G^{\mu\nu} G_{\nu\rho}
		= G_D^{\mu\nu} G^D_{\nu\rho}
			+ G_D^{\mu d}\, e^{2\sigma} A_\rho,
	\end{gather}
	Contract the last equation with $A^\rho$, and we can solve for $G_D^{\mu d}$ and then all other components. 
	Alternatively, we can use the inversion formula for a block matrix\footnote{
		See e.g.~\wikiref{https://en.wikipedia.org/wiki/Block\_matrix\#Block\_matrix\_inversion}{Block matrix \# Block matrix inversion}. 
	}; either way, we obtain a nice and clean result:
	\begin{equation}
		G_D^{\mu d}
		= -A^\mu,\quad
		G_D^{dd}
		= e^{-2\sigma} + A^2,\quad
		G_D^{\mu\nu}
		= G^{\mu\nu},
	\end{equation}
	There is also a formula\footnote{
		See e.g.~\wikiref{https://en.wikipedia.org/wiki/Determinant\#Block\_matrices}{Determinant \# Block matrices}. 
	} for the determinant $G_D$; we have:
	\begin{equation}
		G_D^{-1}
		= G_d^{-1} \pqty{
				e^{-2\sigma}
				+ A^2 - A^2
			}
		= G_d^{-1} e^{-2\sigma},\quad
		G_D
		= G_d\, e^{2\sigma}
	\end{equation}

%	we have:
%	\begin{equation}
%	\begin{aligned}
%		(\Gamma_D)^\lambda_{\mu\nu}
%		&= G_D^{\lambda\rho}\,\Gamma_{\rho\mu\nu}
%			+ G_D^{\lambda d}\cdot
%			\frac{1}{2}\, \pqty\Big{
%				\pdd{\mu} (e^{2\sigma} A_\nu)
%				+ \pdd{\nu} (e^{2\sigma} A_\mu)
%				- 0
%			} \\
%		&= \Gamma^\lambda_{\mu\nu}
%			- A^\lambda e^{2\sigma}
%				\pqty\Big{
%					2A_{(\mu} \pdd{\nu)} \sigma
%					+ \pdd{(\mu} A_{\nu)}
%				},
%	\end{aligned}
%	\end{equation}
%	\begin{equation}
%	\begin{aligned}
%		(\Gamma_D)^d_{\mu\nu}
%		&= G_D^{\rho d}\,\Gamma_{\rho\mu\nu}
%			+ G_D^{dd}\, e^{2\sigma}
%				\pqty\Big{
%					2A_{(\mu} \pdd{\nu)} \sigma
%					+ \pdd{(\mu} A_{\nu)}
%				} \\
%		&= -A_\rho \Gamma^\rho_{\mu\nu}
%			+ (1 + A^2 e^{2\sigma})
%				\pqty\Big{
%					2A_{(\mu} \pdd{\nu)} \sigma
%					+ \pdd{(\mu} A_{\nu)}
%				},
%	\end{aligned}
%	\end{equation}
%	\begin{equation}
%	\begin{aligned}
%		(\Gamma_D)^\lambda_{\mu d}
%		= (\Gamma_D)^\lambda_{d\mu}
%		&= G^{\lambda\rho}\,\Gamma_{\rho\mu d}
%			+ G_D^{\lambda d}\,\Gamma_{d\mu d} \\
%		&= G^{\lambda\rho}\,
%				\pdd{[\mu} \pqty{A_{\rho]} e^{2\sigma}}
%			- A^\lambda\,\tfrac{1}{2}
%				\pdd{\mu} e^{2\sigma} \\
%		&= e^{2\sigma} \pqty\Big{
%				G^{\lambda\rho}\, \pqty{
%						\tfrac{1}{2} F_{\mu\rho}
%						+ 2A_{[\rho} \pdd{\mu]} \sigma
%					}
%				- A^\lambda\,
%					\pdd{\mu} \sigma
%			} \\
%		&= e^{2\sigma} \pqty{
%				\tfrac{1}{2} F\id{_\mu^\lambda}
%				- A_\mu \pd^\lambda \sigma
%			},
%	\end{aligned}
%	\end{equation}
%	\begin{equation}
%	\begin{aligned}
%		(\Gamma_D)^d_{\mu d}
%		= (\Gamma_D)^d_{d\mu}
%		&= e^{2\sigma} \pqty\Big{
%				- A^\rho\, \pqty{
%						\tfrac{1}{2} F_{\mu\rho}
%						+ 2A_{[\rho} \pdd{\mu]} \sigma
%					}
%				+ (e^{-2\sigma} + A^2)\,
%					\pdd{\mu} \sigma
%			} \\
%		&= e^{2\sigma} \pqty{
%				- \tfrac{1}{2} F_{\mu\rho} A^\rho
%				+ A_\mu A^\rho \pdd{\rho} \sigma
%				+ e^{-2\sigma} \pdd{\mu}\sigma
%			},
%	\end{aligned}
%	\end{equation}
%	\begin{equation}
%		(\Gamma_D)^\lambda_{dd}
%		= G_D^{\lambda\rho}\,\Gamma_{\rho dd}
%		= e^{2\sigma} \pd^\lambda \sigma,\quad
%		(\Gamma_D)^d_{dd}
%		= G_D^{d\rho}\,\Gamma_{\rho dd}
%		= A^\lambda e^{2\sigma}
%			\pdd{\rho} \sigma,
%	\end{equation}

	\begin{enumerate}
	\item The Christoffel symbols can hence be calculated explicitly, using the $G^D_{MN}$ components; the Ricci scalar can then be computed with brute force\footnote{
		Reference: \http{www.weylmann.com/kaluza.pdf}, and \textit{Polchinski}, Chapter 8. 
	}; in the end, we have:
	\begin{equation}
		R_D = R_d
			- 2e^{-\sigma}\laplacian e^\sigma
			- \frac{1}{4} e^{2\sigma}
				F_{\mu\nu} F^{\mu\nu},
	\end{equation}
	\vspace*{-.8\baselineskip}
	\begin{equation}
	\begin{aligned}
		S
		&= \frac{1}{2\kappa_0^2}
			\int \dd[D]{x} \sqrt{-G_D}\, R_D \\
		&= \frac{1}{2\kappa_0^2}\cdot 2\pi R
			\int \dd[d]{x} \sqrt{-G_d}\, e^{\sigma}
				R_D \\
		&\sim \frac{\pi R}{\kappa_0^2}
			\int \dd[d]{x} \sqrt{-G_d}\, e^{\sigma}
			\pqty{
				R_d
				- \frac{1}{4} e^{2\sigma}
					F_{\mu\nu} F^{\mu\nu}
			}
	\end{aligned}
	\end{equation}
	Here we've dropped the $
		\laplacian e^\sigma
	$ term in the Einstein--Hilbert action, for it is a total derivative:
	\begin{equation}
		\laplacian e^\sigma
		= \frac{1}{\sqrt{-G_d}}\,
			\pdd{\mu} \pqty{
				\sqrt{-G_d}\, G_d^{\mu\nu}
				\pdd{\nu} e^\sigma
			}
	\end{equation}
	However, if there is a $D$-dimensional dilaton $\Phi$ coupled to gravity: $
		\mcal{L}_D \sim e^{-2\Phi} R_D
	$, then the $
		e^{-2\Phi} \laplacian e^\sigma
	$ term cannot be dropped, since it will contribute a $\Phi$--$\sigma$ coupling term. Here we are setting $\Phi\equiv 0$.

	The $e^\sigma$ factor before $R_d$ can be absorbed by rescaling; first we eliminate the zero mode of $\sigma$ by rescaling the coupling $\kappa_0\to\kappa$:
	\begin{gather}
		\sigma = \sigma_0 + \sigma',\quad
		\ave{\sigma} = \sigma_0,\quad
		\ave{\sigma'} = 0,
	\\
		\frac{1}{\kappa_0^2}\, e^\sigma
		= \frac{1}{\kappa^2}\, e^{\sigma'},\quad
		\kappa
		= \kappa_0\, e^{-\sigma_0/2},
	\end{gather}
	Then we work on the remaining $
		\sigma' = \sigma - \sigma_0
	$. Note that:
	\begin{gather}
		G'_{\mu\nu}
		= e^{2\omega(x)} G_{\mu\nu},\quad
		G'
		= e^{2\omega\cdot d} G,\quad
		G'^{\mu\nu}
		= e^{-2\omega} G^{\mu\nu},
	\\
		R'_d
		= e^{-2\omega} \pqty\Big{
				R_d
				- 2\,(d-1) \laplacian\omega
				- (d-2)(d-1)\,
					\pdd{\mu}\omega\,
					\pd^\mu\omega
			},
	\\[1ex]
		\sqrt{-G}\, e^{\sigma'} R_d
		\sim \sqrt{-G'}\, R'_d
		\sim \sqrt{-G}\, e^{(d-2)\omega} R_d,\quad
		\omega
		= \frac{\sigma'}{d - 2},
	\end{gather}

	Before we proceed, let's first work out the Weyl transformation of the Laplacian:
	\begin{equation}
	\begin{aligned}
		\nabla'^2 \sigma'
		&= \frac{1}{\sqrt{-G'}}\,
			\pdd{\mu} \pqty{
				\sqrt{-G'} G'^{\mu\nu}
				\pdd{\nu} \sigma'
			} \\
		&= \frac{1}{\sqrt{-G}}\,
			e^{-\omega d}\,
			\pdd{\mu} \pqty{
				\sqrt{-G}\,
					e^{+\omega d}
					e^{-2\omega}\,
				G^{\mu\nu}
				\pdd{\nu} \sigma'
			} \\
		&= e^{-\omega d}\,
				(\pdd{\mu} e^{\sigma'})\,
				G^{\mu\nu} \pdd{\nu} \sigma'
			+ e^{-2\omega} \laplacian \sigma' \\
		&= G'^{\mu\nu}
				\pdd{\mu} \sigma'
				\pdd{\nu} \sigma'
			+ e^{-2\omega} \laplacian \sigma' \\
	\end{aligned}
	\end{equation}
	The transformed Ricci scalar can then be rewritten as:
	\begin{equation}
	\begin{aligned}
		R'_d
		&= e^{-2\omega} R_d
			- 2\,\frac{d-1}{d-2}\, e^{-2\omega}
				\nabla^2 \sigma'
			- \frac{d-1}{d-2}\,
				\pdd{\mu}\sigma'\,
				\pd'^\mu\sigma' \\
		&= e^{-2\omega} R_d
			- 2\,\frac{d-1}{d-2}
				\pqty\Big{
					\nabla'^2 \sigma'
					- \pdd{\mu}\sigma'\,
						\pd'^\mu\sigma'
				}
			- \frac{d-1}{d-2}\,
				\pdd{\mu}\sigma'\,
				\pd'^\mu\sigma' \\
		&= e^{-2\omega} R_d
			- 2\,\frac{d-1}{d-2}\,
				\nabla'^2 \sigma'
			+ \frac{d-1}{d-2}\,
				\pdd{\mu}\sigma'\,
				\pd'^\mu\sigma' \\
	\end{aligned}
	\end{equation}

	Again, the $\nabla'^2 \sigma'$ term is a total derivative and can be dropped in the action. In the end, we get:
	\begin{equation}
	\begin{aligned}
		S
		&\sim \frac{\pi R}{\kappa^2}
			\int \dd[d]{x} \sqrt{-G'_d}
			\pqty{
				R'_d
				- \frac{d-1}{d-2}\,
					\pdd{\mu}\sigma'\,
					\pd'^\mu\sigma'
				- \frac{1}{4}
					e^{
						2(\sigma \sidenote{+} \omega)
					} F_{\mu\nu} F'^{\mu\nu}
			}
	\end{aligned}
	\end{equation}
	This is the effective $d$-dimensional theory that we have been looking for, with a gauge field $F_{\mu\nu}$ and a massless dilaton $\sigma'$. Roughly speaking, the dilaton $\sigma'$ can be treated as a Goldstone boson due to the breaking of scale invariance by compactification\footnote{
		For a more careful discussion, see \textit{Polchinski}. See also \https{physics.stackexchange.com/q/138537}. 
	}.

	Following the convention of \textit{Polchinski}, we define $
		A_\mu = R\tilde{A}_\mu,\ %
		\rho = R e^\sigma,\ %
		\rho_0 = \ave{\rho} = R e^{\sigma_0}
	$, then the gravitational and gauge couplings are given by:
	\begin{gather}
		\frac{1}{2\kappa_d^2}
		= \frac{\pi R}{\kappa^2},\quad
		-\frac{1}{4 g_d^2}
		= -\frac{1}{4}\,
			e^{2\ave{\sigma + \omega}} R^2
			\cdot\frac{\pi R}{\kappa^2}
		= -\frac{1}{4}\, e^{2\sigma_0} R^2
			\cdot \frac{1}{2\kappa_d^2},
	\\[.5ex]
		\therefore\quad
		\kappa_d^2
		= \frac{\kappa^2}{2\pi R}
		= \frac{\kappa_0^2}{2\pi \rho_0},\quad
		g_d^2
		= \frac{2\kappa_d^2}{\rho_0^2}
		= \frac{\kappa_0^2}{\pi \rho_0^3},\quad
		\rho_0
		= R e^{\sigma_0}
	\end{gather}

	\item The above mechanism provides a natural theory of gravity and electromagnetism in $d = 4$. Note that the gravitational and gauge couplings are related with the radius of the compact dimension:
	\begin{equation}
		\frac{g_d^2}{\kappa_d^2}
		= \frac{2}{\rho_0^2}
	\end{equation}
	In reality gravity is much weaker than electromagnetism, which means that $\rho_0 \to 0$, or $R\to 0$ if we gauge-fix $\sigma_0 \equiv 0$. In other words, the radius is constrained by the ratio of the couplings:
	\begin{equation}
		R \sim \sqrt{2}\,\frac{\kappa_d}{g_d}
	\end{equation}
	\end{enumerate}
